Estimation de la tendance-cycle avec des méthodes robustes aux points atypiques

### 2025-06-24 Article/article.qmd
language correction

  pdf:
    include-in-header: template/preambule.tex
    keep-tex: true
    classoption: french
    cite-method: biblatex
    pdf-engine: pdflatex
    papersize: A4
    fig-width: 7.5
    fig-height: 3.5
    toc: false # to include abstract first
    fig-pos: 'H'
    geometry:
      - top=2cm
      - bottom=2cm
      - left = 2.5cm
      - right = 2.5cm
  # docx:
  #   number-sections: true
  #   fig-width: 6.3 # 16cm
  #   crossref:
  #     title-delim: "-"
crossref:
  tbl-prefix: table
  fig-prefix: figure
  sec-prefix: section
  eq-prefix: équation
execute: 
  cache: true
lang: fr
echo: false
toc: true
number-sections: true
tbl-cap-location: top
fig-cap-location: top
bibliography: biblio.bib
csl: template/chicago-author-date.csl
author:
  - name: Alain Quartier-la-Tente 
    affiliation: LEMNA
    orcid: 0000-0001-7890-3857
comments: 
    hypothesis:
      theme: clean
---

>>>>

  pdf:
    include-in-header: template/preambule.tex
    keep-tex: true
    classoption: french
    cite-method: biblatex
    pdf-engine: pdflatex
    papersize: A4
    fig-width: 7.5
    fig-height: 3.5
    toc: false # to include abstract first
    fig-pos: 'H'
    geometry:
      - top=2cm
      - bottom=2cm
      - left = 2.5cm
      - right = 2.5cm
  # docx:
  #   number-sections: true
  #   fig-width: 6.3 # 16cm
  #   crossref:
  #     title-delim: "-"
crossref:
  tbl-prefix: table
  fig-prefix: figure
  sec-prefix: section
  eq-prefix: équation
execute: 
  cache: true
lang: fr
language:
 title-block-author-single: Auteur
echo: false
toc: true
number-sections: true
tbl-cap-location: top
fig-cap-location: top
bibliography: biblio.bib
csl: template/chicago-author-date.csl
author:
  - name: Alain Quartier-la-Tente 
    affiliation: LEMNA
    orcid: 0000-0001-7890-3857
comments: 
    hypothesis:
      theme: clean
---
